---
title       : Developing Data Products Class Project
subtitle    : Predicting Child Heights Using Galton Data
author      : Michael Green
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code.r{
  font-size: 14px;
}
pre {
  font-size: 16px
}
</style>

## Overview
<br/>
- The Child Height Predictor App allows users to input parents heights to get a prediction
of a child's fully grown height.<br/>
<br/>

- The app uses the Galton dataset from the HistData package.

<br/>
- The dataset was compiled by Galton in the 1880, and was part of milestone breakthroughs
in statistics including the discovery of the regression to the mean.

---

## The Data

- The dataset consists of 928 rows of child and parent heights.

- Galton multiplied female heights by 1.08. 

- The heights of female children were multiplied by 1.08.

- The parents height in the dataset is the mid-parent height which is the father's height plus the mother's height multiplied by 1.08.



```{r}
library(HistData)
summary(Galton)

```

---

## Using the App
- The app's sidepanel has fields to enter the father's height, the mother's height and the child's sex. All heights are in inches.

- The results panel shows the the calculated mid-parent height and the predicted child's height.

- The user can change the parents heights using a slider for the mother's height and a slider for the father's height.

- The child's sex is entered via a dropdown box.

- The sliders and the dropdown box are reactive fields in shiny. Changes to any of these fields are immediately reflected in the results data.

- The mid-parent height is the father's height + the mother's height * 1.08.

- The child's height is calculated using a regression model. 
A child's predicted height is the intercept + the slope * the mid-parent height.For female children the result is divided by 1.08


---

## Regression Plot


```{r echo=FALSE,simple-plot1, fig.height = 4, fig.align = 'left', message = F}
library(ggplot2)

g <- ggplot(Galton,aes(parent,child))

g + geom_point() + geom_smooth()


```

***

```{r echo=FALSE,simple-plot2, fig.height = 4, fig.align = 'right', message = F}

plot(Galton$child ~ Galton$parent)
abline(lm(child ~ parent,data=Galton))

```

---


## Regression Model


```{r echo=TRUE}
modelFit <- lm(Galton$child ~ Galton$parent)
summary(modelFit) 
```

---
